\documentclass{ximera}

\title{Ratios, Rates and Proportions}
\author{Amy Riordan}

\begin{document}
\begin{abstract}
Ratios, Rates and Proportions video resources from Module 2.
\end{abstract}
\maketitle

\section*{Ratios, Rates and Proportions}

Below each video, you’ll find a set of practice problems. Try those problems first. If you run into any difficulties, go back and rewatch the video, then attempt the problems again. This way, you’ll reinforce what you’ve learned and build a stronger understanding.

\section*{Ratios and Rates}

Ratios and Rates (ERAU|4:08)

\youtube{placeholder}

% filepath: /code/ModuleTwo/ratiosandproportions.tex
% ...existing code...

\section*{Ratios}

\begin{problem}
A recipe calls for 2 cups of flour and 5 cups of sugar. What is the ratio of flour to sugar? $\answer{2:5}$
\begin{feedback}
The ratio of flour to sugar is $2:5$.
\end{feedback}
\end{problem}

\begin{problem}
There are 12 boys and 8 girls in a class. What is the ratio of boys to girls in simplest form? $\answer{3:2}$
\begin{feedback}
The ratio is $12:8$, which simplifies to $3:2$.
\end{feedback}
\end{problem}

\begin{problem}
A bag contains 15 red marbles and 10 blue marbles. What is the ratio of blue marbles to total marbles?  $\answer{2:5}$
\begin{feedback}
Total marbles: $15 + 10 = 25$. The ratio is $10:25$, which simplifies to $2:5$.
\end{feedback}
\end{problem}

% ...existing code...

% filepath: /code/ModuleTwo/ratiosandproportions.tex
% ...existing code...

\section*{Rates}

\begin{problem}
A car travels 180 miles in 3 hours. What is its average speed in miles per hour? $\answer{60}$
\begin{feedback}
Divide distance by time: $180 \div 3 = 60$. The rate is $60$ miles per hour.
\end{feedback}
\end{problem}

\begin{problem}
A factory produces 240 widgets in 8 hours. What is the rate of production in widgets per hour? $\answer{30}$
\begin{feedback}
Divide total widgets by hours: $240 \div 8 = 30$. The rate is $30$ widgets per hour.
\end{feedback}
\end{problem}

\begin{problem}
If a runner completes 5 kilometers in 25 minutes, what is the runner's speed in kilometers per minute? $\answer{0.2}$
\begin{feedback}
Divide distance by time: $5 \div 25 = 0.2$. The rate is $0.2$ kilometers per minute.
\end{feedback}
\end{problem}

% ...existing code...

% filepath: /code/ModuleTwo/ratiosandproportions.tex
% ...existing code...

\section*{Unit Rates}

\begin{problem}
A grocery store sells 6 apples for \$3. What is the unit rate in dollars per apple? $\answer{0.50}$
\begin{feedback}
Divide total cost by number of apples: $3 \div 6 = 0.50$. The unit rate is \$0.50 per apple.
\end{feedback}
\end{problem}

\begin{problem}
A printer can print 120 pages in 8 minutes. What is the unit rate in pages per minute? $\answer{15}$
\begin{feedback}
Divide total pages by minutes: $120 \div 8 = 15$. The unit rate is $15$ pages per minute.
\end{feedback}
\end{problem}

\begin{problem}
A car travels 300 miles on 10 gallons of gas. What is the unit rate in miles per gallon? $\answer{30}$
\begin{feedback}
Divide total miles by gallons: $300 \div 10 = 30$. The unit rate is $30$ miles per gallon.
\end{feedback}
\end{problem}

% ...existing code...

\section*{Proportions}

Proportions (ERAU|3:27)

\youtube{placeholder}

% filepath: /code/ModuleTwo/ratiosandproportions.tex
% ...existing code...

\section*{Proportions}

\begin{problem}
If $\frac{3}{4} = \frac{x}{12}$, what is $x$? $x=\answer{9}$
\begin{feedback}
Cross-multiply: $3 \times 12 = 4x \implies 36 = 4x$. Divide by $4$: $x = 9$.
\end{feedback}
\end{problem}

\begin{problem}
A map uses a scale of $1$ inch $:$ $5$ miles. If two cities are $3$ inches apart on the map, how far apart are they in real life? $x=\answer{15}$ miles
\begin{feedback}
Set up the proportion: $\frac{1}{5} = \frac{3}{x}$. Cross-multiply: $1x = 5 \times 3 \implies x = 15$ miles.
\end{feedback}
\end{problem}

\begin{problem}
Solve for $x$: $\dfrac{15}{40-x} = \dfrac{3}{x}$ $x=\answer{\frac{20}{3} \approx 6.67}$
\begin{feedback}
Cross-multiply: $15x = 3(40 - x)$. Expand: $15x = 120 - 3x$. Add $3x$ to both sides: $18x = 120$. Divide by $18$: $x = \frac{120}{18} = \frac{20}{3} \approx 6.67$.
\end{feedback}
\end{problem}

\begin{problem}
If $8$ pencils cost \$6, how much do $20$ pencils cost? $x=\answer{15}$ dollars
\begin{feedback}
Set up the proportion: $\frac{8}{6} = \frac{20}{x}$. Cross-multiply: $8x = 6 \times 20 \implies 8x = 120$. Divide by $8$: $x = 15$.
\end{feedback}
\end{problem}

\begin{problem}
A recipe calls for $2$ cups of rice for $5$ servings. How many cups are needed for $12$ servings? $x=\answer{4.8}$ cups
\begin{feedback}
Set up the proportion: $\frac{2}{5} = \frac{x}{12}$. Cross-multiply: $5x = 2 \times 12 \implies 5x = 24$. Divide by $5$: $x = 4.8$ cups.
\end{feedback}
\end{problem}

\begin{problem}
If $x:7 = 12:21$, what is the value of $x$? $x=\answer{4}$
\begin{feedback}
Write as a fraction: $\frac{x}{7} = \frac{12}{21}$. Cross-multiply: $21x = 7 \times 12 \implies 21x = 84$. Divide by $21$: $x = 4$.
\end{feedback}
\end{problem}

% ...existing code...

\section*{Applying Proportions}

Applying Proportions (ERAU|5:51)

\youtube{placeholder}

% filepath: /code/ModuleTwo/ratiosandproportions.tex
% ...existing code...

\section*{Applying Proportions}

\begin{problem}
A blueprint uses a scale of $1$ cm $:$ $2$ m. If a wall is $7$ cm long on the blueprint, how long is the actual wall? $x=\answer{14}$ meters
\begin{feedback}
Set up the proportion: $\frac{1}{2} = \frac{7}{x}$. Cross-multiply: $1x = 2 \times 7 \implies x = 14$ meters.
\end{feedback}
\end{problem}

\begin{problem}
A solution contains $5$ grams of salt in $100$ mL of water. How many grams of salt are needed for $350$ mL of water? $x=\answer{17.5}$ grams
\begin{feedback}
Set up the proportion: $\frac{5}{100} = \frac{x}{350}$. Cross-multiply: $100x = 5 \times 350 \implies 100x = 1750$. Divide by $100$: $x = 17.5$ grams.
\end{feedback}
\end{problem}

\begin{problem}
A car travels $120$ miles in $3$ hours. How far will it travel in $5$ hours at the same rate? $x=\answer{200}$ miles
\begin{feedback}
Set up the proportion: $\frac{120}{3} = \frac{x}{5}$. Cross-multiply: $3x = 120 \times 5 \implies 3x = 600$. Divide by $3$: $x = 200$ miles.
\end{feedback}
\end{problem}

\begin{problem}
A photograph is $4$ inches wide and $6$ inches tall. If it is enlarged so the width is $10$ inches, what will be the height? $x=\answer{15}$ inches
\begin{feedback}
Set up the proportion: $\frac{4}{6} = \frac{10}{x}$. Cross-multiply: $4x = 6 \times 10 \implies 4x = 60$. Divide by $4$: $x = 15$ inches.
\end{feedback}
\end{problem}

\begin{problem}
A recipe requires $3$ cups of flour for $8$ cookies. How much flour is needed for $20$ cookies? $x=\answer{7.5}$ cups
\begin{feedback}
Set up the proportion: $\frac{3}{8} = \frac{x}{20}$. Cross-multiply: $8x = 3 \times 20 \implies 8x = 60$. Divide by $8$: $x = 7.5$ cups.
\end{feedback}
\end{problem}

% ...existing code...

\end{document}
